\documentclass[aps,superscriptaddress,twocolumn,nopreprintnumbers,floatfix,groupedaddress]{revtex4-1}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{hyperref}
\usepackage{color,units}
\usepackage{lineno}
\usepackage{xspace}
\usepackage{mathtools}
\usepackage{physics}
\usepackage{acronym}
\usepackage{subfigure}

\newcommand{\bilby}{{\sc Bilby}\xspace}
\newcommand{\lal}{{\sc LAL}\xspace}
\newcommand{\lalsuite}{{\sc LALSuite}\xspace}
\newcommand{\lalsimulation}{{\sc LALSimulation}\xspace}
\newcommand{\sur}{{\sc NRHybSur3dq8}\xspace}
\newcommand{\Z}{\mathcal{Z}}
\newcommand{\M}{\mathcal{M}}
\renewcommand{\L}{\mathcal{L}}
\newcommand{\BF}{\mathcal{BF}}
\newcommand{\proposal}{proposal}
\newcommand{\target}{target}
\newcommand{\ep}[1]{\textcolor{red}{[EP: #1]}}
\newcommand{\et}[1]{\textcolor{blue}{[ET: #1]}}
\newcommand{\ct}[1]{\textcolor{green}{[CT: #1]}}

\newcommand{\nessai}{{\sc Nessai}\xspace}
\newcommand{\vitamin}{{\sc VItamin}\xspace}
\newcommand{\bilbypipe}{{\sc bilby\_pipe}\xspace}
\newcommand{\lalinference}{{\sc LALInference}\xspace}
\newcommand{\dynesty}{{\sc dynesty}\xspace}
\newcommand{\cpnest}{{\sc cpnest}\xspace}
\newcommand{\nflows}{{\sc nflows}\xspace}
\newcommand{\pytorch}{{\sc PyTorch}\xspace}
\newcommand{\corner}{{\sc corner}\xspace}
\newcommand{\matplotlib}{{\sc matplotlib}\xspace}
\newcommand{\seaborn}{{\sc seaborn}\xspace}
\newcommand{\numpy}{{\sc NumPy}\xspace}
\newcommand{\scipy}{{\sc SciPy}\xspace}
\newcommand{\pandas}{{\sc pandas}\xspace}
\newcommand{\python}{{\sc Python}\xspace}
\newcommand{\imrphenomp}{{\sc IMRPhenomPv2}\xspace}


\newcommand{\figwidth}{8.6cm}
\newcommand{\onehalffigwidth}{12.9cm}
\newcommand{\doublefigwidth}{17.2cm}
\newcommand{\montefigwidth}{11cm}

\begin{document}


\acrodef{GW}[GW]{Gravitational wave}
\acrodef{BBH}[BBH]{binary black hole}
\acrodef{EM}[EM]{electromagnetic}
\acrodef{CBC}[CBC]{compact binary coalescence}
\acrodef{BNS}[BNS]{binary neutron star}
\acrodef{NSBH}[NSBH]{neutron star black hole}
\acrodef{PSD}[PSD]{power spectral density}
\acrodef{ELBO}[ELBO]{evidence lower bound}
\acrodef{LIGO}[LIGO]{advanced Laser Interferometer Gravitational wave Observatory}
\acrodef{CVAE}[CVAE]{conditional variational autoencoder}
\acrodef{KL}[KL]{Kullback--Leibler}
\acrodef{GPU}[GPU]{graphics processing unit}
\acrodef{LVC}[LVC]{LIGO-Virgo Collaboration}
\acrodef{PP}[p-p]{probability-probability}
\acrodef{SNR}[SNR]{signal-to-noise ratio}

\break
\pagebreak

However, the way it affects the development of the brain is unclear. Constant repetition of certain actions and experience are reflected in the structure of the brain. For instance, the cerebral cortex of experienced musicians— a region in the cerebrum responsible for motor skills and memory— differs greatly from other people. It can be gleaned that understanding information helps develop a person’s memory. Alternatively, some studies suggest that an important stimulus for brain development is the diversity of incoming data. In this case, comprehending fascinating information from the internet is much better than learning empty facts and figures. However, even web pages are usually overloaded with information to which an individual ’s short-term memory cannot cope with it. This may have a side effect on a person ’s memory system. Apparently, there is no clear perspective of the issue.



However, the way it affects the development of the brain is unclear. Constant repetition of certain actions and experience are reflected in the structure of the brain. For instance, the cerebral cortex of experienced musicians— a region in the cerebrum responsible for motor skills and memory— differs greatly from other people. It can be gleaned that understanding information helps develop a person’s memory. Alternatively, some studies suggest that an important stimulus for brain development is the diversity of incoming data. In this case, comprehending fascinating information from the internet is much better than learning empty facts and figures. However, even web pages are usually overloaded with information to which an individual ’s short-term memory cannot cope with it. This may have a side effect on a person ’s memory system. Apparently, there is no clear perspective of the issue.

However, the way it affects the development of the brain is unclear. Constant repetition of certain actions and experience are reflected in the structure of the brain. For instance, the cerebral cortex of experienced musicians— a region in the cerebrum responsible for motor skills and memory— differs greatly from other people. It can be gleaned that understanding information helps develop a person’s memory. Alternatively, some studies suggest that an important stimulus for brain development is the diversity of incoming data. In this case, comprehending fascinating information from the internet is much better than learning empty facts and figures. However, even web pages are usually overloaded with information to which an individual ’s short-term memory cannot cope with it. This may have a side effect on a person ’s memory system. Apparently, there is no clear perspective of the issue.

However, the way it affects the development of the brain is unclear. Constant repetition of certain actions and experience are reflected in the structure of the brain. For instance, the cerebral cortex of experienced musicians— a region in the cerebrum responsible for motor skills and memory— differs greatly from other people. It can be gleaned that understanding information helps develop a person’s memory. Alternatively, some studies suggest that an important stimulus for brain development is the diversity of incoming data. In this case, comprehending fascinating information from the internet is much better than learning empty facts and figures. However, even web pages are usually overloaded with information to which an individual ’s short-term memory cannot cope with it. This may have a side effect on a person ’s memory system. Apparently, there is no clear perspective of the issue.

However, the way it affects the development of the brain is unclear. Constant repetition of certain actions and experience are reflected in the structure of the brain. For instance, the cerebral cortex of experienced musicians— a region in the cerebrum responsible for motor skills and memory— differs greatly from other people. It can be gleaned that understanding information helps develop a person’s memory. Alternatively, some studies suggest that an important stimulus for brain development is the diversity of incoming data. In this case, comprehending fascinating information from the internet is much better than learning empty facts and figures. However, even web pages are usually overloaded with information to which an individual ’s short-term memory cannot cope with it. This may have a side effect on a person ’s memory system. Apparently, there is no clear perspective of the issue.

However, the way it affects the development of the brain is unclear. Constant repetition of certain actions and experience are reflected in the structure of the brain. For instance, the cerebral cortex of experienced musicians— a region in the cerebrum responsible for motor skills and memory— differs greatly from other people. It can be gleaned that understanding information helps develop a person’s memory. Alternatively, some studies suggest that an important stimulus for brain development is the diversity of incoming data. In this case, comprehending fascinating information from the internet is much better than learning empty facts and figures. However, even web pages are usually overloaded with information to which an individual ’s short-term memory cannot cope with it. This may have a side effect on a person ’s memory system. Apparently, there is no clear perspective of the issue.

However, the way it affects the development of the brain is unclear. Constant repetition of certain actions and experience are reflected in the structure of the brain. For instance, the cerebral cortex of experienced musicians— a region in the cerebrum responsible for motor skills and memory— differs greatly from other people. It can be gleaned that understanding information helps develop a person’s memory. Alternatively, some studies suggest that an important stimulus for brain development is the diversity of incoming data. In this case, comprehending fascinating information from the internet is much better than learning empty facts and figures. However, even web pages are usually overloaded with information to which an individual ’s short-term memory




\end{document}